Computational Luminance Constancy from Naturalistic Images

### 2018-09-13 Revision1/Revision1.tex
edited a word in future directions

In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions, with only matte surfaces in the scenes. It is natural to by studying with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem. In natural scenes, however, there are other sources of variation that add additional richness. These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material (e.g. specularity), and shape as well as lighting geometry. The methods we developed here may be generalized to study the effects of variation in these factors. That is, one could incorporate these other sources of variation into the generation of the scenes and again learn estimators from the corresponding labeled images. A challenge for this approach will be to thoughtfully control the increase in problem complexity, both to keep compute time feasible and to ensure that it is possible to extract meaningful insight from the results. Extending the work to include variation of material may provide insights not only about luminance constancy but also for computations that relate to material perception (see \citeNP{fleming2017material}); extending the work to include variation in object shape and lighting geometry may clarify the role of object boundaries versus object interiors for providing information that supports perception of object color and lightness (see \citeNP{land1971lightness, rudd2016retinex}). We also note that there is a literature on how increasing stimulus complexity along the various lines listed above affects human color and lightness perception (e.g. \citeNP{beck1964effect,yang2001illuminant, yang2002stereo,todd2004lightness, snyder2005illumination, boyaci2003effect, xiao2008surface, kingdom2011lightness, xiao2012color, anderson2015perceptual, toscani2017lightness}), as well as the computational problem of color and lightness constancy (e.g. \citeNP{lee1986method, d1986mechanisms, funt1988color, tominaga1989standard, barron2012color, barron2015convolutional, finlayson2018colour}).

>>>>

In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions, with only matte surfaces in the scenes. It is natural to start with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem. In natural scenes, however, there are other sources of variation that add additional richness. These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material (e.g. specularity), and shape as well as lighting geometry. The methods we developed here may be generalized to study the effects of variation in these factors. That is, one could incorporate these other sources of variation into the generation of the scenes and again learn estimators from the corresponding labeled images. A challenge for this approach will be to thoughtfully control the increase in problem complexity, both to keep compute time feasible and to ensure that it is possible to extract meaningful insight from the results. Extending the work to include variation of material may provide insights not only about luminance constancy but also for computations that relate to material perception (see \citeNP{fleming2017material}); extending the work to include variation in object shape and lighting geometry may clarify the role of object boundaries versus object interiors for providing information that supports perception of object color and lightness (see \citeNP{land1971lightness, rudd2016retinex}). We also note that there is a literature on how increasing stimulus complexity along the various lines listed above affects human color and lightness perception (e.g. \citeNP{beck1964effect,yang2001illuminant, yang2002stereo,todd2004lightness, snyder2005illumination, boyaci2003effect, xiao2008surface, kingdom2011lightness, xiao2012color, anderson2015perceptual, toscani2017lightness}), as well as the computational problem of color and lightness constancy (e.g. \citeNP{lee1986method, d1986mechanisms, funt1988color, tominaga1989standard, barron2012color, barron2015convolutional, finlayson2018colour}).
